AFQ-Insight

### 2019-11-25 reports/manuscript/sections.tex
Add methods section to manuscript

\section{Acknowledgements}

Here are some amazing acknowledgements.

>>>>

\section*{Acknowledgments}

This work was supported by BRAIN Iniative grant 1RF1MH121868-01 from the
National Institutes for Mental Health and by a grant from the Gordon \& Betty
Moore Foundation and the Alfred P. Sloan Foundation to the University of
Washington eScience Institute Data Science Environment. We would like to thank
Scott Murray for a useful discussion of the SGL method.

### 2019-11-25 reports/manuscript/sections/results.tex

The WH dataset used for continuous regression contains data from 76 healthy
subjects, ranging between 6 years and 50 years of age
\cite{yeatman2014lifespan}. SGL fit to tractometry-extracted features in these
subjects accurately predicts the age of the subjects. The model reaches a mean
absolute error of 3.6 years (Figure \ref{fig:regress-results}), which is lower
than the results of a recent study that predicted age in a large sample, based
on TBSS-extracted diffusion features \cite{Richard2018-ux}. The model weights in
this case are distributed over many different tracts and dMRI tissue properties
(Figure \ref{fig:regress-beta}) This demonstrates that SGL is not coerced to
produce overly sparse results when a more accurate model requires a dense
selection of features.

>>>>

The WH dataset used for continuous regression contains data from 76 healthy
subjects, ranging between 6 years and 50 years of age
\cite{yeatman2014lifespan}. SGL was fit to tractometry-extracted features: FA
and MD in 20 major brain tracts, with each tract divided into 100 nodes. To
evaluate the fit of the model, we used a nested cross-validation procedure. In
this procedure, batches of subjects are held out. For each batch (or fold), the
model is fully fit without this data. Then, once the parameters are fixed, the
model is inverted to predict the ages of held out subjects based on the linear
coeffiecients and the static non-linearity. data is held out, and a model age
was predicted using a model that was fit without that subject. This scheme
automatically finds the right level of regularization and fits the coefficients
to the ill-posed linear model, while guarding against overfitting. SGL
accurately predicts the age of the subjects in this procedure, with procedure,
with a mean absolute error of 3.6 years (Figure \ref{fig:regress-results}),
which is lower than the results of a recent study that predicted age in a large
sample, based on TBSS-extracted diffusion features \cite{Richard2018-ux}. The
model weights in this case are distributed over many different tracts and dMRI
tissue properties (Figure \ref{fig:regress-beta}) This demonstrates that SGL is
not coerced to produce overly sparse results when a more accurate model requires
a dense selection of features.
